---
title: "Objective 2"
output: html_document
---

this document is base on [this post](http://www.sthda.com/english/wiki/two-way-anova-test-in-r)

Is there difference in mean total energy cost for different types of settlements and year of construction?

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load data, packages...

```{r}
library(dplyr)
library(ggpubr)
library(car)

energy <- read.csv('../../data/recs2009_public_vlad_clean.csv')
```

Prepare factors and dependent variable

```{r}
energy$TOTALDOL.log <- log(energy$TOTALDOL)
energy$YEARMADERANGE.f <- factor(energy$YEARMADERANGE,
                                 levels = c(1, 2, 3, 4, 5, 6, 7, 8),
                                 labels = c("<1950", "1950-1959", "1960-1969", "1970-1979", "1980-1989", "1990-1999", "2000-2004", "2005-2009"))
energy$UR.f <- factor(energy$UR)
```

Lets see whether our data is balanced...

```{r}
table(energy$YEARMADERANGE.f, energy$UR.f)
```

Nope, it is not. Now let's plot 2 levels...

```{r}
p <- ggboxplot(energy, x = "YEARMADERANGE.f", y = "TOTALDOL.log", color = "UR.f",
          palette = c("#00AFBB", "#E7B800"))
p + rotate_x_text(angle = 90) + labs(x = "Year when housing unit was built", y="Total cost log, in whole dollars")
p <- ggline(energy, x = "YEARMADERANGE.f", y = "TOTALDOL.log", color = "UR.f",
       add = c("mean_se"),
       palette = c("#00AFBB", "#E7B800"))
p + rotate_x_text(angle = 90) + labs(x = "Year when housing unit was built", y="Total cost log, in whole dollars")
```

Do we need non-additive model?

```{r}
energy.aov3 <- aov(TOTALDOL.log ~ YEARMADERANGE.f*UR.f, data = energy)
summary(energy.aov3)
Anova(energy.aov3, type = "III")
```

Nope!!!

```{r}
energy.aov2 <- aov(TOTALDOL.log ~ YEARMADERANGE.f + UR.f, data = energy)
summary(energy.aov2)
Anova(energy.aov2, type = "III")
```

Display residuals and QQ plot

```{r}
plot(energy.aov3, 1)
plot(energy.aov3, 2)
```

What are these outliers?

```{r}
energy[c(11947, 9767, 1310),]
```

Bummer. But I think we simply have too big sample for this test.